Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-07-24 response_2.txt

Reviewer A

>*The annotation guidelines are needed to ensure replicability. Add them as
appendix material.

We've added the English guidelines, though we note the guidelines are not really a contribution of this work, much of its content was created as part of Brooke et al. 2015 (though there was some editing, additions, and consolidations, and well as translations into other languages and adaptions to language specific phenomena).

@@

> *In table 5 these examples include a lot of noise. Can the authors comments
how to decide on the criteria for rejecting something as FS.

There is of course some noise, but based on our analysis the noise is fairly consistent with the precision numbers in our evaluation (i.e. most of the ICWSM examples are good FS, whereas about half of the BNC are). Hopefully including the guidelines help with this, since we don't feel its possible to give succinct explanation of how to decide whether something is an FS: though there are several tests discussed in the guidelines, at the core we are always reliant on native speaker intuition about whether a sequence of words is produced as a unit, i.e. Wray's definition as given at the beginning of Section 2.

> -"that do not scale to the large corpora,"
-"allows for indi- vidual morphemes be part"
-"Define terms Trev, Taff, Q, etc in the algorithm  "
-Add information about the size of the Croatian corpus
-Table4, the By length % figures don't sum to 100
-"of a article"
-"to an good FS"
-"of the them"
-"In Section 2, we noted than FS"
-"inflectional flex- ibilty"
-Introduce abbreviation for " the LPR decomp approach "
-"that it is consistently outperforms"
-In the conclusions the authors refer to MWE lexicons, instead of FS
lexicons.

We have addressed all this except the abbreviation for LPR decomp (not sure why this necessary beyond what we have already done?) and the last point, which we believe is based on a misunderstanding. In the conclusion (and the introduction and title) we talk about "multiword lexicons", which is not the same as MWE lexicon, it is intended to be a more general term including FS lexicons as well as MWE lexicons.

@@

Reviewer B

> - For readers familiar with machine learning notation, it would be more
intuitive to use y throughout for the variables to be predicted, namely the
binary activation states of n-gram nodes. It may also be more intuitive to
use x instead of t for each "input" (n-gram node). Then covering could be
defined more explicitly as max{0, (c(x)-\sum_{i \in parents(x)} y_i *
c(x_i))/c(x)}, and likewise for other equations. The optimization problem
could be stated formally by wrapping argmax_{y,C} around eq. (1).

We have integrated this suggestion, though not to full extent you have suggested (i.e. no argmax), since it creates other issues with the presentation.

@@

>- I was a bit confused about the definition of "overlap" at the type vs.
token level: at first I thought the graph was constructed with each node
having its own corpus frequency information, but there are mentions of
counting overlaps in a corpus, and these counts are presumably associated
with edges between type-overlapping nodes. Showing frequency counts in
figure 2 may help clarify this. From figure 2, I assume at a type level, two
nodes overlap if at least one word is shared between the two n-grams, but
neither set of words is a superset of the other (which would be
subsumption), and a gap counts as a special word for determining subsumption
vs. overlap ("keep everything under wraps" and "keep * under wraps" merely
overlap), but two n-grams must share more than a gap to count as
overlapping. Is the ordering of tokens significant for determining overlap?

We've added some clarification of this point. Overlap at the type level consists exactly of the count of token overlaps in the corpus. Two n-grams types might share words at the type level, but are considered overlapping only when there is at least one token in the corpus which belong to an instance of each type (there is no measure of the degree). ol() is exactly the number of times there is such a overlap.

Related to this, we realized that we had left out the important point that subsumed n-grams are considered to trivially overlap with subsuming n-grams for the purposes of counting their overlap score when both are on (in addition to the covering and clearing effects which occur when one of the two nodes is off). The reverse, though, is not true, since that would basically prohibit any two subsuming nodes from turning on (since the count of subsumed node is always larger than the subsuming one).

Reviewer C

@@

> - In some place, the paper is not an easy read -- I found a few
expressions that were fairly cryptic even for a seasoned reviewer in
NLP, examples include: "the best (i.e., most parsimonious) explanation
for statistical irregularities due to lexical affinity": what does
"parsimonious explanation", "lexical affinity" (S.1), or "explainedness"
of a node (S.3) mean? I would like to see a more formal definition right
where this concepts are introduced.

The word "parsimonious" is used here in its typical, non-technical sense to refer to explanations which cover the data and yet are as simple as possible. It's used in the introduction, and is just intended to give a sense to the reader of what is to come, in terms of the logic of the model. Since its not a term, nor does it pretend to be, we don't think there's a problem here.

We have excised the term "lexical affinity", which was intended to point at the predictability that remains after syntactic predictability is removed in the denominator of LPR, but is admittedly rather cryptic in the introduciton, and is never returned to.

@@

"Explainedness" gets an informal explanation just after its introduction in Section 3, and then more formal definition later (3.3). An earlier draft had expainedness defined immediately, but this required forward pointers to node interaction functions, which the other reviewers disliked. There's a certain amount of interconnectedness here that makes it impossible to fully satisfy the need to define everything formally up front.

> - Section 2: I found the discussion of formulaic sequence vs. multi-word
generally interesting but could not understand how this distinction
plays a role in the task you are trying to address and the model you
present -- it is frustating for a reviewer to try to follow a one-page
discussion on exact terminology and then jump to the presentation of
related work by noticing that is not that important to understand it
("Regardless of the terminology used..."). An evil reviewer could think
that you try to account for FS because they are easier to handle in your
model: what would be the results on a FS vs. MWE dataset?

"Regardless of the terminology used..." is not intended to imply that the terminology is not important, just that core methodologes used for multiword lexicon creation are somewhat independant of them. We have reworded this.

@@

The point of that section is to be clear about what we are doing, and how it relates to other work in NLP, where the default term for the targets of this sort of extraction is MWE. The fact that semantic non-compositionality is not core to the definition of FS is in fact very important in terms of the model we have built. The FS versus MWE distinction is quite important relevant to the motivation discussed at the end of that section.

In the discussion, we briefly consider exactly the FS versus MWE distinction you mention. The answer is that our model is quite good at identifying MWE (better than non-MWE FS), but it will of course identify some non-MWE FS, and so applying it directly to MWE dataset would result in apparently low precision.

>- Section 3: there are a plethora of lexical association measures from
the literature, why using LPR? Also, why using the minimum LPR as
opposed to the product (Brooke et al., 2015). I found your explanation
in the paper rather tentative...

There are a plethora of lexical association measures, but as we already note the the backgound section, very few scale to gapped n-grams of unrestricted length (some have no formulation beyond two words, others do, but are exponential in the statistics that must be collected as n increases). Those that do scale do quite poorly at the general task, as shown here with raw counts and PMI; as we mention in the experiment section, other work which has compared our baseline models here with a wider range of such measures. LPR was specifically designed for FS identification and showed good results in earlier work, and in the last paragraph of Section 3.1, we very talk explicitly about why minLPR is a good measure for this particular use (i.e. the lattice), where each movement up a layer of the lattice involves adding a single word, which is what the minLPR metric is focusing on.

@@

>- Section 3.2 why cherry-picking the threshold for hard covering to 2/3
or $C$ in the range [3, 6] as opposed to tune on dev data? Same for the
hyperparameter in the bullet list at the end of 3.4?

"Cherry-picking" suggests we are just picking the best values for our test set, which is certainly not the case. All of the hyperparameters you mention were in fact subject to some early evaluation on development data and then fixed from that point on. We did not rigorously tune them in the machine learning sense, which is perhaps what you mean by "cherry picking"; we wanted to avoid supervision as much as possible, and tuning of that kind is a form of supervision. We picked reasonable values, saw that they worked using a small amount of development data, and moved on. We've removed the reference to [3 ,6] since it seems to have lead to this misinterpretation: we did some post hoc evaluation of what values of C caused the model performance to drop drastically, but that was unrelated to the selection of 4 as our C value, which happened very early in development.

@@

>- Section 3.4: why not looking also at other node visiting strategies?
E.g., random?

We did test a few options on dev data (based on n-gram length and LPR; not random, though, because we wanted to preserve the deterministic nautre of the model), and decided on count-based sorting. However, we don't think this is interesting or important enough to include as a focus in the paper.

@@

>- Section 4: there exists a plethora of datasets for MWE, why not
comparing with other datasets: how were the dataset chosen? Also, why
not using corpora for the same language of different sizes (cf. e.g.,
Riedl and Biemann)?

By datasets, do you mean MWE vocabularies? or MWE corpora like the STREUSLE? We're not sure exactly what you mean, since no corpus annotated with MWE could possibly have the quantity of data required to build an unsupervised model like this. In terms of evaluation, the main reason not to use existing MWE datasets is exactly that, we are not doing traditional MWE extraction, but rather FS extraction; the existing MWE datasets have at best very inconsistent treatment of nonMWE FS, generally. Though it is possible to use MWE datasets for FS evaluation, see Brooke et al. (2015) who derived a test set from STREUSLE (results were entirely consistent with the results using the FS set we also use here), it requires some hackiness that we felt was indefensible for our main evaluation. Note we did include a small, targeted evaluation of recall using STREUSLE in the discussion.  We addressed this issue rather thoroughly in the previous reviewer response.

It is worth mentioning (and we've added a small note to the paper) that we do prefer social media and mixed genre corpora, which have linguistic diversity and therefore a much more interesting range of FS pheonomena. Since you mention Reidl and Bieman, one criticim we have of that work was that it was focused on extremely specific, technical corpora, and not particularly representative of general FS (or MWE) phenomena across the language as whole.

We in fact do have corpora of very different sizes for English, namely the ICWSM and BNC (which is about a tenth the size). Perhaps you mean taking smaller version of the same corpus and seeing the effect of data size? This would be interesting, but it's not a trivial addition, since our test sets are sampled from the corpus; subsampling the corpus would require creating new test sets for that smaller corpus.

@@

- Section 6: When discussing "the time needed to build and optimize the
lattice" it would be good to add exact run-time figures

This is a reasonable idea, but we don't feel entirely confident reporting exact runtime figures due to difficulty in creating a controlled environment sufficient (i.e. DP-seg takes over 10 days to run on the BNC, and we can't ensure that our server stays otherwise unused) as well as the fact we can't control for the implementation of the comparison techniques. More generally, to set up runtime comparisons properly requires more of a digression than we really want to make at that point in the paper. Instead, we've hedged our discussion of runtime a bit.
